\documentclass[12pt]{article}

%%%%%%%%%%%%
% packages %
%%%%%%%%%%%%
\usepackage[hmargin=0.5in,vmargin=1in]{geometry}
\usepackage{hyperref}
% \usepackage[onehalfspacing]{setspace}
\usepackage{tikz}
\usepackage{xcolor}

\definecolor{blue}{RGB}{98,119,204}
\definecolor{red}{RGB}{153,0,0}
\definecolor{brown}{RGB}{153,77,0}
\definecolor{green}{RGB}{0,153,0}
\definecolor{MyBackground}{RGB}{250,255,255}

%%%%%%%%%%%%%%%%%
% user commands %
%%%%%%%%%%%%%%%%%

\setlength{\parskip}{0.25cm}

%%%%%%%%%%%%
% document %
%%%%%%%%%%%%
\begin{document}

% make smaller title
\begin{center}
    \large
    {\bfseries Teaching statement, July 2026} \\
    Willard Robinson \\
    PhD student, Department of Economics, North Carolina State University
\end{center}

\smallskip

\noindent Curiosity is the ultimate motivator. During my time as a student, I have had many teachers encourage my curiosity, and through this curiosity I have learned the most. My major goal in teaching is to continue that tradition while helping students see the world as a space full of incentives, strategies, and rationalizations. I am grateful to have had the opportunity to practice this teaching during my time as a graduate student, and I find providing real-world examples and using intuition are my most effective tools. By practicing these in the classroom, I have found that my research, too, benefits from the inclusion of plain words reasoning and parsimonious examples.

My best lectures are built around the whiteboard and audience participation. For example, when teaching the tradable permits model in my environmental economics course, I work through stylized examples of trading emissions permits between two firms with their own marginal abatement cost schedules. The class and I discuss how much money firm $A$ is willing to pay for one more emissions permit. Then, we determine how much money firm $B$ is willing to accept to sell one of its permits. Together, we discuss whether a trade can be made between the two firms. By writing each sequential trade on the board, we create a history of trades between the two firms. After we reach a point where no more trading can occur, I use this history of trades to trace out the marginal abatement curves and the demand curve for emissions permits. These examples are simple enough that, with a little guidance, the students could ``solve'' them on their own. The benefit of working together is that it helps the students bring that thought process to the front of their minds.

My research benefits my teaching. I had the uncommon opportunity to be the sole instructor of an undergraduate course in my field, and I was able to use my own research as examples in class. When teaching emissions trading systems, I was able to intuitively explain to my students how introducing carbon offsets can act as a cost reduction to the regulated firms. When teaching nonmarket valuation, I used my angler recreation paper as an example of the travel cost method. Being familiar with these concepts in practice greatly improves my ability to teach them in intuitive ways.

If given the opportunity, I would 


\section*{Teaching experience}

During graduate school, I was a teaching assistant (TA) for three different courses---including both graduate and undergraduate subjects---and the instructor for the environmental economics course. In all of these courses, I made a concerted effort to stoke genuine intellectual curiosity in all students, and to continuously focus on becoming a better teacher.


\begin{itemize}
    \item \textbf{Principles of Microeconomics} (\textbf{TA:} Fall 2022, Spring 2023, Fall 2023): \\
    In many cases, this is the first and only experience undergraduates have with economics. My responsibilities included leading three 50-minute recitation sections of 30--40 students once each week, holding office hours, grading group problem sets, and acting as the first student point of contact for students regarding these. The recitations included a brief discussion of a concept from earlier in the week, followed by applications of the subject with my guidance. According to evaluations, students consider the recitations a crucial part of the course. During my third semester, I was the ``Head TA'' for this class, which included writing problem sets and supporting other TAs.
    \item \textbf{Introduction to Resource and Environmental Economics} (\textbf{TA:} Fall 2023, Spring 2025; \textbf{Instructor:} Fall 2025): \\
    This is the only undergraduate course focused on environmental and resource economics. It covers topics such as property rights, non-market goods, externalities, and public goods. My responsibilities as a TA included grading problem sets and exams, holding office hours, and participating in online class discussions. As an instructor, I planned the semester's syllabus, created and graded all course material, and was the sole point of contact for all students. 
    \item \textbf{Microeconomics II} (\textbf{TA:} Spring 2024): \\
    This is the second course in the PhD sequence in Microeconomics. My responsibilities as a TA included grading problem sets and exams, holding regular review sessions, and holding weekly office hours. This class taught advanced material including general equilibrium, social choice theory, game theory, and mechanism design. Problem sets were intensive and required extensive discussion with students.
\end{itemize}

\end{document}